P4IRS: A Code Generation Framework for Parallel and Performance-Portable Particle Simulations

### 2025-05-06 sage_latex_template/manuscript.tex
minor
Signed-off-by: Rafael Ravedutti <rafael.r.ravedutti@fau.de>

\RMchange{
The final step of the P4IRS compiler is the code generation, which converts the optimized \ac{IR} to low-level hardware assembly instructions or to another high-level language (source-to-source compilation).
In its current state, P4IRS generates C++ and CUDA code with MPI for distributed-memory parallelism, but new backend languages, intermediate representations and technologies can be included without difficulties by extending the code generator.
Although most of the code generation is straightforward for the \ac{IR} in its lowest level, there are some important points that are important to handle different backends and achieve performance-portability.

>>>>

\RMchange{
The final step of the P4IRS compiler is the code generation, which converts the optimized \ac{IR} to low-level hardware assembly instructions or to another high-level language (source-to-source compilation).
In its current state, P4IRS generates C++ and CUDA code with MPI for distributed-memory parallelism, but new backend languages, intermediate representations and technologies can be included without difficulties by extending the code generator.
Although most of the code generation is straightforward for the \ac{IR} in its lowest level, there are important aspects that must be considered to handle different backends and achieve performance-portability.
